# INTRODUCTION
Das ist ein Test [@Roth_2014].

# METHODS

## Study Area
We worked in a **beautiful** place with lots of trees, like *Quercus suber* and *Laurus nobilis*.


## Data collection and analysis
```{r read_data, eval = FALSE, echo = FALSE}
dataset <- read.csv("mydata.csv")
```

```{r model, echo = FALSE, eval = FALSE}
model <- lm(y ~ x)
```

We used the statistical language `R`. 



# RESULTS
Trees in forest A grew taller than those in forest B (mean height: `r mean(25, 31, 28)` versus `r mean(13, 19, 16)` m). And many more cool results that get updated dynamically.


# DISCUSSION
Discuss.


# ACKNOWLEDGEMENTS

# REFERENCES
<div id = "refs"></div>
\eleft
\clearpage


\listoftables
\newpage

```{r Table1, results='asis', echo=FALSE, cache=FALSE}
kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.")
```

\clearpage


\listoffigures
\newpage

```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```


\clearpage

```{r sessioninfo, echo = FALSE, eval = TRUE}
sessionInfo()
```
